Example penalized LTRC survival model with simulated data

### 2021-07-20 example.Rmd
Minor edits to prose in example

# Model fitting
## Model data
### Input matrix
`glmnet` requires an input matrix `x`, which which must be a `matrix` object. Here we consider a simple example with a small number of predictors contained in `x`.

@@

### Response
When fitting Cox proportional hazards models with `glmnet`, the response should be a `survival::Surv` object. The key difference between modeling LTRC and RC data, is that the response must contain start-stop intervals when using LTRC data. Start-stop `Surv` object are created by passing the time that a patient enters the dataset (`time`), the follow-up time (`time2`), and a status indicator equal to 1 if a patient has died and 0 if they are alive.

@@

## Cross validation
We will fit a penalized Lasso model appropriate for LTRC data using `cv.glmnet()` (note: requires `glmnet` > 4.1). The value of the tuning parameter$\lambda$ that minimizes the partial likelihood deviance (`lambda.min`) is selected using 5-fold cross validation. For more details, see the vignette on the [glmnet website](https://glmnet.stanford.edu/articles/Coxnet.html).

@@

Plots using base `R` graphics can quickly be generated using the `plot.survfit()` method, which produces a survival curve for each patient in the test set.

@@

Note that we could have alternatively used a general purpose plotting package like `ggplot` or specialized plotting package for survival analysis like `survminer` to produce more modern looking graphics. It might also be a good idea to aggregate predicted survival curves across patients in a meaningful way.

### Calibration
While there are many great `R` packages such a `rms` and `pec` that can be used to evaluate a survival model (including for calibration), none (to our knowledge) work with LTRC data. We consequently wrote our own function to calibrate survival models for the paper (available in the file `R/calibrate.R`), which we will use here. `calibrate()` is a generic function with a method for `survfit` objects. We also created a generic `autplot()` method to quickly plot the output produced by `calibrate()`.

>>>>

# Model fitting
## Model data
### Input matrix
`glmnet` requires an input matrix `x`, which must be a `matrix` object. Here we consider a simple example with a small number of predictors contained in `x`.

@@

### Response
When fitting Cox proportional hazards models with `glmnet`, the response should be a `survival::Surv` object. The key difference between modeling LTRC and RC data is that the response must contain start-stop intervals when using LTRC data. Start-stop `Surv` objects are created by passing the time that a patient enters the dataset (`time`), the follow-up time (`time2`), and a status indicator equal to 1 if a patient has died and 0 if they are alive.

@@

## Cross validation
We will fit a penalized lasso model appropriate for LTRC data using `cv.glmnet()` (note: requires `glmnet` > 4.1). The value of the tuning parameter $\lambda$ that minimizes the partial likelihood deviance (`lambda.min`) is selected using 5-fold cross validation. For more details, see the vignette on the [glmnet website](https://glmnet.stanford.edu/articles/Coxnet.html).

@@

Plots using base `R` graphics can be quickly generated using the `plot.survfit()` method, which produces a survival curve for each patient in the test set.

@@

Note that we could have alternatively used a general purpose plotting package like `ggplot` or a specialized plotting package for survival analysis like `survminer` to produce more modern looking graphics. It might also be a good idea to aggregate predicted survival curves across patients in a meaningful way.

### Calibration
While there are many great `R` packages such a `rms` and `pec` that can be used to evaluate a survival model (including via calibration), none (to our knowledge) work with LTRC data. We consequently wrote our own function to calibrate survival models for the paper (available in the file `R/calibrate.R`), which we will use here. `calibrate()` is a generic function with a method for `survfit` objects. We also created a generic `autplot()` method to quickly plot the output produced by `calibrate()`.
